---
title: "French given names per year per department"
author: "Lucas Mello Schnorr, Jean-Marc Vincent"
date: "October, 2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# The environment
library(tidyverse)
library(ggplot2)

version
```
The aim of the activity is to develop a methodology to answer a specific question on a given dataset. 

The dataset is the set of Firstname given in France on a large period of time. 
[given names data set of INSEE](https://www.insee.fr/fr/statistiques/fichier/2540004), we choose this dataset because it is sufficiently large, you can't do the analysis by hand, the structure is simple


You need to use the _tidyverse_ for this analysis. Unzip the file _dpt2019_txt.zip_ (to get the **dpt2019.csv**). Read in R with this code. Note that you might need to install the `readr` package with the appropriate command.

## Download Raw Data from the website
```{r}
file = "dpt2020_txt.zip"
if(!file.exists(file)){
  download.file("https://www.insee.fr/fr/statistiques/fichier/2540004/dpt2020_csv.zip",
	destfile=file)
}
unzip(file)
```

## Build the Dataframe from file
```{r}
FirstNames <- read_delim("dpt2020.csv",delim =";")
FirstNames
```
Translation in english of variables names: 
sexe -> gender 
preusuel (prénom usuel) -> Firstname
annais (année de naissance) -> Birth year
dpt (département) -> department (administrative area unit)
nombre -> number

All of these following questions may need a preliminary analysis of the data, feel free to present answers and justifications in your own order and structure your report as it should be for a scientific report.

```{r}
# Let's replace accents by noramlized letters
normalize_text <- function(text) {
  text = toupper(iconv(text,from="UTF-8",to="ASCII//TRANSLIT"))
  text = str_replace_all(text, "[^[:alnum:]]", "")
  return(text)
}
FirstNames$preusuel_norm = normalize_text(FirstNames$preusuel)
```

1. Choose a firstname and analyse its frequency along time. Compare several firstnames frequency
```{r}
plot_evolution <- function (firstname_to_analyze) {
  firstname_to_analyze_norm = normalize_text(firstname_to_analyze)
  n_occurences <- FirstNames[FirstNames$preusuel_norm == firstname_to_analyze_norm,] %>% group_by(annais) %>% summarise(Nombre = sum(nombre))
  plot(n_occurences, main=paste("Evolution for ", firstname_to_analyze))
}
plot_evolution("jean-pierre")
plot_evolution("Théo")
plot_evolution("mohamed")
```
2. Establish, by gender, the most given firstname by year. 

```{r}
most_given_male_name <- FirstNames[FirstNames$sexe == 1,] %>% 
  filter(preusuel_norm != "PRENOMSRARES") %>%
  filter(annais != "XXXX") %>%
  drop_na(annais) %>%
  group_by(annais, preusuel_norm) %>%
  summarize(Nombre = sum(nombre)) %>%
  slice(which.max(Nombre))
most_given_female_name <- FirstNames[FirstNames$sexe == 2,] %>% 
  filter(preusuel_norm != "PRENOMSRARES") %>%
  filter(annais != "XXXX") %>%
  drop_na(annais) %>%
  group_by(annais, preusuel_norm) %>%
  summarize(Nombre = sum(nombre)) %>%
  slice(which.max(Nombre))
print(most_given_male_name)
print(most_given_female_name)
```
3. Make a short synthesis
??
4. Advanced (not mandatory) : is the firstname correlated with the localization (department) ? What could be a method to analyze such a correlation.

The report should be a pdf knitted from a  notebook (around  3 pages including figures), the notebook and the report should be delivered.